\textls[-0]{\thetitle}

### 2023-03-22 casestudies.tex
Update statistics about FPOP for STLC.

%The current plugin implementation does not yet support
%mutually inductive types or mutual induction, which are
%useful for modeling languages much more complex than STLCs.
%However,
%we believe accommodating mutually inductive types does
%not pose theoretical challenges.

>>>>

%The current plugin implementation does not yet support
%mutually inductive types or mutual induction, which are
%useful for modeling languages much more complex than STLCs.
%However,
%we believe accommodating mutually inductive types does
%not pose theoretical challenges.
When programming in a direct style, before using FPOP, the STLC base module 
will take around 350LOCs, and STLC with one feature is around 400 LOCs, because
it requires to repeat the definition of the STLC base definition. It will take 
more space when we add more features into STLC.

After using FPOP, the 
STLC base family also take about 350 LOCs. However, one feature as children family takes only about 100~250 LOCs. What's more, the mixin of two features usually only take 1~20 LOCs.
